Efficient Calculation of Polynomial Features on Sparse Matrices

### 2016-02-13 paper/workshop/sparse_poly.tex
fixed johns address
fixed abstract

\author{Andrew Nystrom \\
Savvysherpa Inc.\\
6200 Shingle Creek Pkwy \\
Suite 400 \\
Minneapolis, MN 55430, USA \\
\texttt{awnystrom@gmail.com} \\
\And
John Hughes \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
}

@@

\begin{abstract}
We provide an algorithm for polynomial feature expansion that can operate directly on sparse a
matrix. For a vector $\vec{x}$ of a $N \times D$ matrix, the algorithm has time and space complexity $O(d^kD^k)$ where $k$ is the polynomial order and $d$ is the density of $\vec{X}$.

>>>>

\author{Andrew Nystrom \\
Savvysherpa Inc.\\
6200 Shingle Creek Pkwy \\
Suite 400 \\
Minneapolis, MN 55430, USA \\
\texttt{awnystrom@gmail.com} \\
\And
John Hughes \\
Department of Computer Science \\
Brown University \\
Providence, RI \\
\texttt{jfh@cs.brown.edu} \\
}

@@

\begin{abstract}
We provide an algorithm for polynomial feature expansion that can operate directly on sparse a
matrix. For a vector $\vec{x}$ of a $N \times D$ matrix, the algorithm has time and space complexity $O(d^kD^k)$ where $k$ is the polynomial order and $d$ is the density of $\vec{x}$.
